Exploratory Data Analysis for College Scorecard Dataset

### 2017-02-21 Draft-xuezhou-sjb.Rmd
fix formats and depress the messages from output

---
title: "Draft-assinment1"
author: "Kun Shen, Xiang Li, Xue Zhou"
date: "February 10, 2017"
output: html_document
---

```{r setup, include=FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
```

@@

#need to be commented out 
class(as.data.frame(apply(variable[,-c(2,3,4,8)],2,as.numeric)))

@@

write.csv(data_clean,"data_clean.csv")
```
The data_clean will be the cleaned dataset we used in the further variable summaries and comparisons

For numeric variabls, we calculate the basic summary statistics such as median, min, max, mode and quantile. We also use visualizations such as hisgroms and boxplots to understand the distribution of the values. For categorical variables, we use frequency table to understand the frequcies of each categories. Box chart is used as a visualization tool.

@@

```
The frequency table counts the number of records belonging to each state, since each records represents a institution, each cell also equals to the number of university in that state.

@@

```{r, message=FALSE}
prop.table(table(data_clean$`PREDDEG_factor`)) * 100
data_clean %>% ggplot(aes(x=PREDDEG_factor, fill = 'blue')) + 
  geom_histogram(stat = "count") +
  xlab("Degree")  +
  ylab('Count') +
  ggtitle('Number of Institution in Each Predominant Degree type') +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=20, hjust=0.5)) 
```
From above frequency table, we see that about 5% of the population are unclassified in terms of the predomiant degree they offer.  43.2% offer Certificate degree as their predominant degree, 27.3% predominantly offer Bachelor degree and only 4.23% are classified as Graduate degree predominant.

@@

  ggplot(data=data_clean , aes(PAR_ED_PCT_1STGEN)) + 
    geom_histogram(breaks=seq(0.1, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage first-generation students") +
    labs(x="PAR_ED_PCT_1STGEN", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```
From the histogram, we can tell the share of first generarion students is most frequently falling into the range between 0.5 and 0.6. The value with the value more than 0.8 are rare. The colleges with the share of first generarion students value less than 0.5 are much more than the ones with the value larger than 0.5. Thus the histogram is seriously left skewed.

@@

```
From the summary results, we learned that the maximum value of the variable is $87,414, which is for Aerosim Flight Academy located in FL. while the minimum value is about $-19,360 - the value for Berea College located in KY. Considering the elements are collected from Title IV institutions, we reasoned that the negative values may be due to the fact that some intituions's finainal aid supoort can cover the students' all the costs, meanwhile overbalancing the cost amount. There are not much differerences between mean value and median value, which is around $15,000. We can conclude that the average net price costs for most institutuins are falling into the this range. The standard deviation value is 7604.884 which is relatively large, indicating a great spread in the data.

@@

  #histogram for NPT_COM
  ggplot(data=data_clean , aes(NPT4_COMBINE)) + 
    geom_histogram(breaks=seq(0, 90000, by =2000), 
                   col="red", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage first-generation students") +
    labs(x="NPT_COM", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```
From the histogram, we notice that the average net cost for IV institutions typically is 16000 -18000. The values between 16000 - 20000 are quite frequent. There were an unsually lagrge number of costs. The institutions with cost of more than 50000 were atypical. Due to the atypical large value, the histogram is abviously right skewed. Without those extreme values, the histogram would be reasonably symmetric.

@@

```
From the summary results, we learned that the maximum value of the variable is 98.56%(Capella University) while the minimum value is about 0.73%(University of Notre Dame). From the mean value, we can tell that about in most colleges, around 56% of the students are financially independent. The standatd deviation value of 23.3% indicates a relative high different among different colleges, which can also be concluded from the difference between maximum value and minimum value. Below is the code to generate a visual representation in the histgram.

@@

  #histogram for NPT_COM
  ggplot(data=data_clean , aes(DEP_STAT_PCT_IND)) + 
    geom_histogram(breaks=seq(0.1, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage of students who are financially independent") +
    labs(x="DEP_STAT_PCT_IND", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```
From the histogram, we notice that the value between 0.7 to 0.8 are quite frequent. There was no obvious extrme value in the sample, thus the histogram is normally distributed.

@@

```
From the output, we can tell that the range is between 0 to 100%.	No students in Thunderbird School of Global Management has received the Pell grant while all of the students in American Conservatory Theater have receiced the Pell Grant. Among the colleges in the sample, half colleges have this rate as high as 52.7% (median value of 52.7%), which means more than half of undergraduare students are able to receive the Pell Grant to cover their costs. The standard deviation value is 22.57%,  indicating a relative high difference of this element among different colleges, which can also be noticed from the largest range (100%). Below is the code to generate a visual representation in the histgram.

@@

  ggplot(data=data_clean , aes(PCTPELL)) + 
    geom_histogram(breaks=seq(0, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage of undergraduates who receive a Pell Grant") +
    labs(x="PCTPELL", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```
From the histogram, we are able to conclude that in most colleges, 40% to 50% of the undergraduate students are able to receive the Pell Grant. With little skewness, the histogram is resonalbe symmetric.

@@

```
From the output, we can tell that the range is between 0 to 100%.	As we can recall from the previous variable(PCTPELL), American Conservatory Theater has both the PCTLOAN and PCTPELL the value of 100%. Gadsden State Community College has no students reveiced federal loans in the given year. Among the colleges in the sample, half colleges have this rate as high as 60.08% , which means around 60% of undergraduare students are able to receive the fedaral student loans. The standard deviation value is 29.26%,  indicating a relative high difference of this element among different colleges, which can also be noticed from the largest range (100%). Below is the code to generate a visual representation in the histgram.

@@

  ggplot(data=data_clean , aes(PCTFLOAN)) + 
    geom_histogram(breaks=seq(0, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percent of all federal undergraduate students receiving a federal student loan") +
    labs(x="PCTFLOAN", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```
From the histogram, it's obvious that there are two peaks in the graph. The rates between 0- 10% and the rates between 60% to 80% are similarly frequent compated to the other ranges.

@@

```
From the output, we can tell that the highest value is 48,250 - Southwest University of Visual Arts-Tucson, while the lowest value is 1448 - South Florida Institute of Technology. From the median value of 14000, we can tell that among the colleges in the sample, the students who have completed the deducaiton from half of them had the median loan debt of 14000. The standard deviation value is 8020.958,  indicating a relative high difference of this element among different colleges. Below is the code to generate a visual representation in the histgram.

@@

```
From the histogram, it is obvious that most students in the sampled colleges still have 8000- 10000 debt amount after they completed the education. This amount is related to the federal loan amount provided by each institution. Additionally, it is asscociated with students' ability to repay the loan during the acdemic period. For example, for the students who were capabiblity of working through the acedemic years or securing jobs before graduation may have a less value for this variable.

@@

```
We use summary statistics, standard deviation and histogram to understand the distribution of this variable. The summary statistics show that students in 50% of institution have a median debt of more than 5500, which is not very unaffordable. The median debt for attending students can be as much as 27620 for some school and as low as 600 for others, which indicates it may have a large variance. So we also calculate standard deviation to measure the dispersion of the distribution. The standard deviation is 2415.623 about 95% of institution have a median debt ranging from 1167.754  to 10830.246. The histogram shows that the distribution of the median roughly follows a standard distribution with a sharp peak and slightly heavy tail.

@@

```
From the output, we can tell that the highest value is 155,606.6 -Jewish Theological Seminary of America, while the lowest value is 0 -Associated Technical College-Los Angeles. From the median value of 19,262.26, we can tell that among the colleges in the sample, the students in half of them had the family income below 19,262.26	. The standard deviation value is 18,824.31,  indicating a relative high difference of this element among different colleges. Below is the code to generate a visual representation in the histgram.

@@

```
Baesd on the output, we can see the highest median value for avreage net price exists in DC while the lowest median value is in AS(American Samoa).Moreover, we found that the top 5 states are DC, VT, MA, NH, RI, which are all states conceiving amount of well-known educational institutions.

@@

```
From the result, the Private Nonprofit institutions and Public institutions have a similar low median values while the provate For- profit institutions have a hgihest value. This is resonable because generally speanking, the private for-profit colleges may have much higher costs than the private nonprofit and public institutions. The low-income students were more likely to seek a Pell Grant for assistant. Additionally, in some states, state financial aid may be sufficient to cover costs at community colleges; thus the students in thoes schools may not need to seek for addtional financial aid like Pell Grant.

@@

ggplot(data_clean, aes(x=PCTPELL, fill=Control_factor)) + geom_histogram(alpha=0.9, position="identity") +
  labs(title="Overlaying histogram between PCTPELL and Control ") +
    theme(plot.title = element_text(hjust = 0.5))

```
From the overlaying histograms, the percentage of students who receive Pell Grant are quite frequent for Private For-profit institutions between 0.7 and 0.75 ; the percentage of students who receive Pell Grant are quite frequent around 0.4 for Public institutions and Private Nonprofit institutions. The histogram for private for profit is slightly left skewed due to atypical small value near 0. The histogram for public and private nonprofit institions are reasonably symmetric

##6.4. The relationship between Percentage first-generation students and States<a id="6.4"></a>
To compare the Percentage first-generation students with the different states, we grouped data into the state level to take a further analysis.We would like to investigate the percentage of first-generation students based on the status distribution.

@@

```
From the scatter plot, it is obvious that the MD_FAMINC is in a negative linear relationship with PCTPELL: the data show a downhill pattern from left to right; As the MD_FAMINC increase, the value of PCTPELL decreases. It makes sense in the real world applcation: for institutions with low percentage of students who receive the Pell Grant, the financial aids like Pell Grant may not be as necessary as they are in the instituions with high value of PCTPELL, thus these collges students will tend to have a high median family income after they graduate.

@@

```
From the result, we can tell the highest median value is in Privately For-profit colleges, which means that in most private for-profit colleges, the students are more likely to be financial independent.

@@

```
First, we use scatter plot to visualize the relationship between earning and the amount of debts, the plot clearly shows a positive relationship. Then we further calculate pearson correlation to confirm our hypothesis. The resulting coefficient 0.44 indicatesa moderate linear relationship between earning and debts.

@@

```
A scatter plot is created to visualize the relationship between these two variables. From the chart, we see the earning seems to show a decreasing trend as the default rate increases, which shows a negative relationship between earning and default rate. Then we calculate the correlation coefficient between these two variables. The resulting r = -0.33 shows that correlation between earning and default rate is negative but the relationship is not very strong, which may be due to the influences of some outliers. To conclude, the negative relationship between earning and default rate of loan repayment needs extra data to confirm.

@@

```
Mean value of the earning is more representative for the two categories, preF and ctrF. For the range of average earning, the darkest color shows the lowest earning, while the lightest color shows the highest value. According to the plot, we realize that ???Private For-profit college??? whose predominant degree award is ???Graduate degree??? has the lowest average earning with the minimum average value at \$3100, while ???Public college??? whose predominant degree award is ???Graduate degree??? has the highest average earning with the maximum average value at $45850.

@@

```
According to the histogram comparison of predominant degree award among three types of colleges, we realize that for public college, Associate???s-degree is most frequent awarded in the public colleges. Bachelor???s-degree is most frequent awarded in the private nonprofit colleges. Certificate-degree is most frequent awarded in private for-profit colleges.

@@

```
```{r}
summary(data_clean$MD_EARN_WNE_P6[data_clean$Control_factor=="Public"])
summary(data_clean$MD_EARN_WNE_P6[data_clean$Control_factor=="Private Nonprofit"])
summary(data_clean$MD_EARN_WNE_P6[data_clean$Control_factor=="Private For-profit"])
```
Obvious differences contain in these three boxplots. The boxplot of ???Public college??? is comparatively short, while the boxplot of ???Private Nonprofit??? is comparatively tall. The ???Private For-profit college??? has the lowest median earning.

>>>>

---
title: "Exploratory Data Analysis for College Scorecard Dataset"
author: "Kun Shen, Xiang Li, Xue Zhou"
date: "February 20, 2017"
output: html_document
---

```{r setup, include=FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message = FALSE)
```

@@

@@

write.csv(data_clean,"data_clean.csv")
```

The data_clean will be the cleaned dataset we used in the further variable summaries and comparisons.For numeric variabls, we calculate the basic summary statistics such as median, min, max, mode and quantile. We also use visualizations such as hisgroms and boxplots to understand the distribution of the values. For categorical variables, we use frequency table to understand the frequcies of each categories. Box chart is used as a visualization tool.

@@

The frequency table counts the number of records belonging to each state, since each records represents a institution, each cell also equals to the number of university in that state.

@@

```{r, message=FALSE}
prop.table(table(data_clean$`PREDDEG_factor`)) * 100
data_clean %>% ggplot(aes(x=PREDDEG_factor, fill = 'blue')) + 
  geom_histogram(stat = "count") +
  xlab("Degree")  +
  ylab('Count') +
  ggtitle('Number of Institution in Each Predominant Degree type') +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=20, hjust=0.5)) 
```

From above frequency table, we see that about 5% of the population are unclassified in terms of the predomiant degree they offer.  43.2% offer Certificate degree as their predominant degree, 27.3% predominantly offer Bachelor degree and only 4.23% are classified as Graduate degree predominant.

@@

  ggplot(data=data_clean , aes(PAR_ED_PCT_1STGEN)) + 
    geom_histogram(breaks=seq(0.1, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage first-generation students") +
    labs(x="PAR_ED_PCT_1STGEN", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```

From the histogram, we can tell the share of first generarion students is most frequently falling into the range between 0.5 and 0.6. The value with the value more than 0.8 are rare. The colleges with the share of first generarion students value less than 0.5 are much more than the ones with the value larger than 0.5. Thus the histogram is seriously left skewed.

@@

From the summary results, we learned that the maximum value of the variable is $87,414, which is for Aerosim Flight Academy located in FL. while the minimum value is about $-19,360 - the value for Berea College located in KY. Considering the elements are collected from Title IV institutions, we reasoned that the negative values may be due to the fact that some intituions's finainal aid supoort can cover the students' all the costs, meanwhile overbalancing the cost amount. There are not much differerences between mean value and median value, which is around $15,000. We can conclude that the average net price costs for most institutuins are falling into the this range. The standard deviation value is 7604.884 which is relatively large, indicating a great spread in the data.

@@

  #histogram for NPT_COM
  ggplot(data=data_clean , aes(NPT4_COMBINE)) + 
    geom_histogram(breaks=seq(0, 90000, by =2000), 
                   col="red", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage first-generation students") +
    labs(x="NPT_COM", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```

From the histogram, we notice that the average net cost for IV institutions typically is 16000 -18000. The values between 16000 - 20000 are quite frequent. There were an unsually lagrge number of costs. The institutions with cost of more than 50000 were atypical. Due to the atypical large value, the histogram is abviously right skewed. Without those extreme values, the histogram would be reasonably symmetric.

@@

From the summary results, we learned that the maximum value of the variable is 98.56%(Capella University) while the minimum value is about 0.73%(University of Notre Dame). From the mean value, we can tell that about in most colleges, around 56% of the students are financially independent. The standatd deviation value of 23.3% indicates a relative high different among different colleges, which can also be concluded from the difference between maximum value and minimum value. Below is the code to generate a visual representation in the histgram.

@@

  #histogram for NPT_COM
  ggplot(data=data_clean , aes(DEP_STAT_PCT_IND)) + 
    geom_histogram(breaks=seq(0.1, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage of students who are financially independent") +
    labs(x="DEP_STAT_PCT_IND", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```

From the histogram, we notice that the value between 0.7 to 0.8 are quite frequent. There was no obvious extrme value in the sample, thus the histogram is normally distributed.

@@

From the output, we can tell that the range is between 0 to 100%.	No students in Thunderbird School of Global Management has received the Pell grant while all of the students in American Conservatory Theater have receiced the Pell Grant. Among the colleges in the sample, half colleges have this rate as high as 52.7% (median value of 52.7%), which means more than half of undergraduare students are able to receive the Pell Grant to cover their costs. The standard deviation value is 22.57%,  indicating a relative high difference of this element among different colleges, which can also be noticed from the largest range (100%). Below is the code to generate a visual representation in the histgram.

@@

  ggplot(data=data_clean , aes(PCTPELL)) + 
    geom_histogram(breaks=seq(0, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percentage of undergraduates who receive a Pell Grant") +
    labs(x="PCTPELL", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```

From the histogram, we are able to conclude that in most colleges, 40% to 50% of the undergraduate students are able to receive the Pell Grant. With little skewness, the histogram is resonalbe symmetric.

@@

From the output, we can tell that the range is between 0 to 100%.	As we can recall from the previous variable(PCTPELL), American Conservatory Theater has both the PCTLOAN and PCTPELL the value of 100%. Gadsden State Community College has no students reveiced federal loans in the given year. Among the colleges in the sample, half colleges have this rate as high as 60.08% , which means around 60% of undergraduare students are able to receive the fedaral student loans. The standard deviation value is 29.26%,  indicating a relative high difference of this element among different colleges, which can also be noticed from the largest range (100%). Below is the code to generate a visual representation in the histgram.

@@

  ggplot(data=data_clean , aes(PCTFLOAN)) + 
    geom_histogram(breaks=seq(0, 1, by =0.1), 
                   col="white", 
                   aes(fill=..count..),na.rm=TRUE)+
    labs(title="Histogram for Percent of all federal undergraduate students receiving a federal student loan") +
    labs(x="PCTFLOAN", y="Count") +
    theme(plot.title = element_text(hjust = 0.5))
```

From the histogram, it's obvious that there are two peaks in the graph. The rates between 0- 10% and the rates between 60% to 80% are similarly frequent compated to the other ranges.

@@

From the output, we can tell that the highest value is 48,250 - Southwest University of Visual Arts-Tucson, while the lowest value is 1448 - South Florida Institute of Technology. From the median value of 14000, we can tell that among the colleges in the sample, the students who have completed the deducaiton from half of them had the median loan debt of 14000. The standard deviation value is 8020.958,  indicating a relative high difference of this element among different colleges. Below is the code to generate a visual representation in the histgram.

@@

From the histogram, it is obvious that most students in the sampled colleges still have 8000- 10000 debt amount after they completed the education. This amount is related to the federal loan amount provided by each institution. Additionally, it is asscociated with students' ability to repay the loan during the acdemic period. For example, for the students who were capabiblity of working through the acedemic years or securing jobs before graduation may have a less value for this variable.

@@

We use summary statistics, standard deviation and histogram to understand the distribution of this variable. The summary statistics show that students in 50% of institution have a median debt of more than 5500, which is not very unaffordable. The median debt for attending students can be as much as 27620 for some school and as low as 600 for others, which indicates it may have a large variance. So we also calculate standard deviation to measure the dispersion of the distribution. The standard deviation is 2415.623 about 95% of institution have a median debt ranging from 1167.754  to 10830.246. The histogram shows that the distribution of the median roughly follows a standard distribution with a sharp peak and slightly heavy tail.

@@

From the output, we can tell that the highest value is 155,606.6 -Jewish Theological Seminary of America, while the lowest value is 0 -Associated Technical College-Los Angeles. From the median value of 19,262.26, we can tell that among the colleges in the sample, the students in half of them had the family income below 19,262.26	. The standard deviation value is 18,824.31,  indicating a relative high difference of this element among different colleges. Below is the code to generate a visual representation in the histgram.

@@

Baesd on the output, we can see the highest median value for avreage net price exists in DC while the lowest median value is in AS(American Samoa).Moreover, we found that the top 5 states are DC, VT, MA, NH, RI, which are all states conceiving amount of well-known educational institutions.

@@

From the result, the Private Nonprofit institutions and Public institutions have a similar low median values while the provate For- profit institutions have a hgihest value. This is resonable because generally speanking, the private for-profit colleges may have much higher costs than the private nonprofit and public institutions. The low-income students were more likely to seek a Pell Grant for assistant. Additionally, in some states, state financial aid may be sufficient to cover costs at community colleges; thus the students in thoes schools may not need to seek for addtional financial aid like Pell Grant.

@@

ggplot(data_clean, aes(x=PCTPELL, fill=Control_factor)) + geom_histogram(alpha=0.9, position="identity") +
  labs(title="Stacked Histogram between PCTPELL and Control ") +
    theme(plot.title = element_text(hjust = 0.5))

From the overlaying histograms, the percentage of students who receive Pell Grant are quite frequent for Private For-profit institutions between 0.7 and 0.75 ; the percentage of students who receive Pell Grant are quite frequent around 0.4 for Public institutions and Private Nonprofit institutions. The histogram for private for profit is slightly left skewed due to atypical small value near 0. The histogram for public and private nonprofit institions are reasonably symmetric

##6.4. The relationship between Percentage first-generation students and States<a id="6.4"></a>
To compare the Percentage first-generation students with the different states, we grouped data into the state level to take a further analysis. We would like to investigate the percentage of first-generation students based on the status distribution.

@@

From the scatter plot, it is obvious that the MD_FAMINC is in a negative linear relationship with PCTPELL: the data show a downhill pattern from left to right; As the MD_FAMINC increase, the value of PCTPELL decreases. It makes sense in the real world applcation: for institutions with low percentage of students who receive the Pell Grant, the financial aids like Pell Grant may not be as necessary as they are in the instituions with high value of PCTPELL, thus these collges students will tend to have a high median family income after they graduate.

@@

From the result, we can tell the highest median value is in Privately For-profit colleges, which means that in most private for-profit colleges, the students are more likely to be financial independent.

@@

First, we use scatter plot to visualize the relationship between earning and the amount of debts, the plot clearly shows a positive relationship. Then we further calculate pearson correlation to confirm our hypothesis. The resulting coefficient 0.44 indicatesa moderate linear relationship between earning and debts.

@@

A scatter plot is created to visualize the relationship between these two variables. From the chart, we see the earning seems to show a decreasing trend as the default rate increases, which shows a negative relationship between earning and default rate. Then we calculate the correlation coefficient between these two variables. The resulting r = -0.33 shows that correlation between earning and default rate is negative but the relationship is not very strong, which may be due to the influences of some outliers. To conclude, the negative relationship between earning and default rate of loan repayment needs extra data to confirm.

@@

Mean value of the earning is more representative for the two categories, preF and ctrF. For the range of average earning, the darkest color shows the lowest earning, while the lightest color shows the highest value. According to the plot, we realize that ???Private For-profit college??? whose predominant degree award is ???Graduate degree??? has the lowest average earning with the minimum average value at \$3100, while ???Public college??? whose predominant degree award is ???Graduate degree??? has the highest average earning with the maximum average value at $45850.

@@

According to the histogram comparison of predominant degree award among three types of colleges, we realize that for public college, Associate???s-degree is most frequent awarded in the public colleges. Bachelor???s-degree is most frequent awarded in the private nonprofit colleges. Certificate-degree is most frequent awarded in private for-profit colleges.

@@

```
```{r}
summary(data_clean$MD_EARN_WNE_P6[data_clean$Control_factor=="Public"])
summary(data_clean$MD_EARN_WNE_P6[data_clean$Control_factor=="Private Nonprofit"])
summary(data_clean$MD_EARN_WNE_P6[data_clean$Control_factor=="Private For-profit"])
```

Obvious differences contain in these three boxplots. The boxplot of ???Public college??? is comparatively short, while the boxplot of ???Private Nonprofit??? is comparatively tall. The ???Private For-profit college??? has the lowest median earning.
